Social inequality in mortality among adults and elderly in northern Sweden 1851--2013\footnote{Paper presented at the session 'Health and Mortality in Arctic Populations'. The Ninth International Congress on Arctic Social Sciences, Umeå, June 8--12, 2017}

### 2017-07-03 icass.Rnw
add Yihui's float suggestions in preamble
nothing done

\usepackage{float}

@@

@@

<<readalldata>>=
## Load remote data:
con <- url("http://capa.ddb.umu.se/data/vb0.rda")
##load("data/vb0.rda")
load(con)
close(con)
vb0$hisclass[is.na(vb0$hisclass)] <- 4
vb0$hisclass <- factor(vb0$hisclass, labels = c("elite", "middle", "worker", "NA"))
##
con <- url("http://capa.ddb.umu.se/data/vb.rda")
##load("data/vb.rda")
load(con)
close(con)
##
con <- url("http://capa.ddb.umu.se/data/lisaold.rda")
##load("data/lisaold.rda")
load(con)
close(con)
##
con <- url("http://capa.ddb.umu.se/data/loTab.rda")
load(con)
close(con)
loTab$period <- factor(loTab$period)
##
vb0Tab <- aggregate(vb0[, c("event", "exposure")],
                   vb0[, c("sex", "age", "period", "cohort",
                          "urban", "civst", "hisclass")],
                   FUN = sum)
vb0Tab$age <- factor(vb0Tab$age)
@

@@

<<lissyoung3>>=
library(eha)
library(xtable)
liss4064 <- loTab[loTab$age < 64.5, ]
con <- url("http://capa.ddb.umu.se/data/lisaold.rda")
##load("data/lisaold.rda")
load(con)
close(con)
@

>>>>

%\usepackage{float}

@@

\renewcommand{\textfraction}{0.05}
\renewcommand{\topfraction}{0.8}
\renewcommand{\bottomfraction}{0.8}
\renewcommand{\floatpagefraction}{0.75}

@@

<<readalldata>>=
## Load remote data:
##con <- url("http://capa.ddb.umu.se/data/vb0.rda")
load("data/vb0.rda")
##load(con)
##close(con)
vb0$hisclass[is.na(vb0$hisclass)] <- 4
vb0$hisclass <- factor(vb0$hisclass, labels = c("elite", "middle", "worker", "NA"))
##
##con <- url("http://capa.ddb.umu.se/data/vb.rda")
load("data/vb.rda")
##load(con)
##close(con)
##
##con <- url("http://capa.ddb.umu.se/data/lisaold.rda")
load("data/lisaold.rda")
##load(con)
##close(con)
##
##con <- url("http://capa.ddb.umu.se/data/loTab.rda")
##load(con)
##close(con)
load("data/loTab.rda")
loTab$period <- factor(loTab$period)
##
vb0Tab <- aggregate(vb0[, c("event", "exposure")],
                   vb0[, c("sex", "age", "period", "cohort",
                          "urban", "civst", "hisclass")],
                   FUN = sum)
vb0Tab$age <- factor(vb0Tab$age)
@

@@

<<lissyoung3>>=
library(eha)
library(xtable)
liss4064 <- loTab[loTab$age < 64.5, ]
##con <- url("http://capa.ddb.umu.se/data/lisaold.rda")
##load("data/lisaold.rda")
##load(con)
##close(con)
@
